Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.00

### 2019-02-22 manuscript.Rmd
text updates

Furthermore we also

>>>>

# Organoid retina differential gene expression versus fetal tissue identifies sets of genes relating to patterning (HOXB family), cell adhesion (protocadherin family), and retinal ganglion function (BRN3/POU4F, NEFL, GAP43, SNCG)

While organoid and retina tissues are highly similar at a pan-transcriptome level, differential expression analysis between organoid and fetal retina reveals differences in related groups of genes.
